---
title: "{{< iconify ph users-three >}} Demographics"
format: html
---

```{r}
#| include: false
library(dashboardr)
```

```{=html}
<style>
/* Ensure chart containers expand to fit content - aggressive overrides */
.cell-output-display,
.cell-output,
.panel-tabset-tabby > .tab-content,
.panel-tabset > .tab-content,
.tab-pane,
.tab-pane.active,
.card-body,
.quarto-figure,
section {
  overflow: visible !important;
  height: auto !important;
  max-height: none !important;
}
/* Ensure highcharts containers respect their set height */
.highcharts-container,
.html-widget,
.htmlwidget {
  overflow: visible !important;
}
</style>
<script>
// Aggressive reflow for Highcharts - multiple attempts to catch widget initialization
(function() {
  function reflowCharts() {
    if (typeof Highcharts !== 'undefined' && Highcharts.charts) {
      Highcharts.charts.forEach(function(chart) {
        if (chart) {
          try { chart.reflow(); } catch(e) {}
        }
      });
    }
  }
  
  // Try multiple times at different intervals
  [0, 100, 250, 500, 1000, 2000].forEach(function(delay) {
    setTimeout(function() {
      window.dispatchEvent(new Event('resize'));
      requestAnimationFrame(reflowCharts);
    }, delay);
  });
  
  // Also reflow on any tab click
  document.addEventListener('click', function(e) {
    if (e.target.matches('.nav-link, [data-bs-toggle="tab"]')) {
      setTimeout(reflowCharts, 50);
    }
  });
})();
</script>
```

## Demographic Targeting Analysis

Explore how advertisers target different demographic groups. This reveals strategic decisions about which audiences receive the most advertising attention.

**Age targeting** shows investment across different generations, while **gender targeting** reveals any differences in how campaigns reach men vs. women.


```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load required libraries
library(dashboardr)
library(dplyr)
library(highcharter)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load multiple datasets

# Load age_data
age_data <- readRDS('age_data_6obs.rds')
cat('age_data loaded:', nrow(age_data), 'rows,', ncol(age_data), 'columns\n')

# Load gender_data
gender_data <- readRDS('gender_data_2obs.rds')
cat('gender_data loaded:', nrow(gender_data), 'rows,', ncol(gender_data), 'columns\n')

```


```{r}
#| echo: false
#| results: 'asis'
dashboardr::render_value_box_row(list(
  list(
    title = "Age Groups Targeted",
    value = "6",
    bg_color = "#2563eb",
    logo_url = NULL,
    logo_text = NULL
  ),
  list(
    title = "Top Age Group",
    value = "35-44",
    bg_color = "#7c3aed",
    logo_url = "ph:trophy",
    logo_text = NULL
  ),
  list(
    title = "Gender Categories",
    value = "2",
    bg_color = "#0891b2",
    logo_url = "ph:gender-intersex",
    logo_text = NULL
  )
))
```

## Demographics


::: {.panel-tabset}

### Age


```{r demographics-age}
# Age Group Targeting Analysis
result <- create_bar(
  data = age_data,
  title = "Age Group Targeting Analysis",
  horizontal = TRUE,
  x_var = "age_group",
  weight_var = "spend",
  subtitle = "How advertisers allocate their budgets across different age demographics. Reveals which age groups receive the most advertising attention.",
  y_label = "Ad Spend (USD)",
  tooltip_prefix = "💰 Spend: $",
  tooltip_suffix = " targeting this age group"
)

result
```


### Gender


```{r demographics-gender}
# Gender Targeting Analysis
result <- create_bar(
  data = gender_data,
  title = "Gender Targeting Analysis",
  horizontal = TRUE,
  x_var = "gender",
  weight_var = "spend",
  subtitle = "Budget allocation across gender demographics. Shows how advertisers prioritize different gender audiences.",
  y_label = "Ad Spend (USD)",
  tooltip_prefix = "💰 Spend: $",
  tooltip_suffix = " targeting this gender"
)

result
```


:::

