---
title: "{{< iconify ph currency-dollar >}} Spending"
format: html
---

```{r}
#| include: false
library(dashboardr)
```

```{=html}
<style>
/* Ensure chart containers expand to fit content - aggressive overrides */
.cell-output-display,
.cell-output,
.panel-tabset-tabby > .tab-content,
.panel-tabset > .tab-content,
.tab-pane,
.tab-pane.active,
.card-body,
.quarto-figure,
section {
  overflow: visible !important;
  height: auto !important;
  max-height: none !important;
}
/* Ensure highcharts containers respect their set height */
.highcharts-container,
.html-widget,
.htmlwidget {
  overflow: visible !important;
}
</style>
<script>
// Aggressive reflow for Highcharts - multiple attempts to catch widget initialization
(function() {
  function reflowCharts() {
    if (typeof Highcharts !== 'undefined' && Highcharts.charts) {
      Highcharts.charts.forEach(function(chart) {
        if (chart) {
          try { chart.reflow(); } catch(e) {}
        }
      });
    }
  }
  
  // Try multiple times at different intervals
  [0, 100, 250, 500, 1000, 2000].forEach(function(delay) {
    setTimeout(function() {
      window.dispatchEvent(new Event('resize'));
      requestAnimationFrame(reflowCharts);
    }, delay);
  });
  
  // Also reflow on any tab click
  document.addEventListener('click', function(e) {
    if (e.target.matches('.nav-link, [data-bs-toggle="tab"]')) {
      setTimeout(reflowCharts, 50);
    }
  });
})();
</script>
```

[← Back to World Map](../index.html#)

# Netherlands Political Advertising Dashboard

## Comprehensive Analysis of Digital Political Advertising

This dashboard provides an **in-depth analysis** of political advertising spending and targeting strategies in Netherlands. Explore how advertisers invest their budgets across different demographics, locations, and interest groups.

### 🎯 Key Insights Available

- **Top Advertisers**: See who's spending the most on political ads
- **Targeting Methods**: Understand how budgets are allocated across targeting strategies
- **Demographics**: Explore age and gender targeting patterns
- **Geographic Focus**: Discover which locations receive the most ad spend
- **Interest Targeting**: See what behaviors and interests are being targeted

### 💡 How to Use This Dashboard

**Hover over any chart element** to see detailed tooltips with spending amounts, percentages, rankings, and contextual information. Use the navigation tabs above to explore different aspects of the advertising data.

*Data from: December 17, 2025 • Spending in USD*

```{r, echo=FALSE, results='asis'}
dashboardr::enable_inputs()
```

```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load required libraries
library(dashboardr)
library(dplyr)
library(highcharter)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data
data <- readRDS('dataset_small_20obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

# Create filtered datasets
# Each filter is applied once and reused across visualizations

data_filtered_690d02e6 <- data %>% dplyr::filter(party == "Government")
data_filtered_613ded75 <- data %>% dplyr::filter(party == "Other")
data_filtered_0ab23edd <- data %>% dplyr::filter(party == "Political Parties")

```


```{r}
#| echo: false
#| results: 'asis'
dashboardr::render_value_box_row(list(
  list(
    title = "Total Ad Spending",
    value = "$2.7M",
    bg_color = "#2563eb",
    logo_url = NULL,
    logo_text = NULL
  ),
  list(
    title = "Total Ads",
    value = "18K",
    bg_color = "#7c3aed",
    logo_url = NULL,
    logo_text = NULL
  ),
  list(
    title = "Advertisers",
    value = "654",
    bg_color = "#0891b2",
    logo_url = NULL,
    logo_text = NULL
  ),
  list(
    title = "Avg Spend/Ad",
    value = "$149",
    bg_color = "#ea580c",
    logo_url = NULL,
    logo_text = NULL
  )
))
```


```{r}
#| echo: false
#| results: 'asis'
dashboardr::render_input_row(list(
  list(
    input_id = "advertiser_filter",
    label = "Filter Advertiser:",
    type = "select_multiple",
    filter_var = "party_name",
    options = NULL,
    options_from = "party_name",
    default_selected = NULL,
    placeholder = "Select...",
    width = "600px",
    min = 0,
    max = 100,
    step = 1,
    value = NULL,
    show_value = TRUE,
    inline = TRUE,
    toggle_series = NULL,
    override = FALSE,
    labels = NULL,
    size = "md",
    help = NULL,
    disabled = FALSE,
    mt = NULL,
    mr = NULL,
    mb = NULL,
    ml = NULL
  )
), style = "boxed", align = "center")
```

## By Party


::: {.panel-tabset}

### Total


```{r by-party-total}
# Top Advertisers by Spending
result <- create_bar(
  data = data,
  title = "Top Advertisers by Spending",
  horizontal = TRUE,
  x_var = "advertiser",
  weight_var = "total_spend",
  subtitle = "Hover for detailed spending breakdown including budget share, ad counts, and rankings",
  y_label = "Total Spend (USD)",
  tooltip_prefix = "💰 Spend: $",
  tooltip_suffix = " USD"
)

result
```


### Government


```{r by-party-government}
# Government
result <- create_bar(
  data = data_filtered_690d02e6,
  title = "Government",
  horizontal = TRUE,
  x_var = "advertiser",
  weight_var = "total_spend",
  tooltip_prefix = "💰 Spend: $",
  tooltip_suffix = " USD"
)

result
```


### Other


```{r by-party-other}
# Other
result <- create_bar(
  data = data_filtered_613ded75,
  title = "Other",
  horizontal = TRUE,
  x_var = "advertiser",
  weight_var = "total_spend",
  tooltip_prefix = "💰 Spend: $",
  tooltip_suffix = " USD"
)

result
```


### Political Parties


```{r by-party-political-parties}
# Political Parties
result <- create_bar(
  data = data_filtered_0ab23edd,
  title = "Political Parties",
  horizontal = TRUE,
  x_var = "advertiser",
  weight_var = "total_spend",
  tooltip_prefix = "💰 Spend: $",
  tooltip_suffix = " USD"
)

result
```


:::

