---
title: "{{< iconify ph target >}} Targeting"
format: html
---

```{r}
#| include: false
library(dashboardr)
```

```{=html}
<style>
/* Ensure chart containers expand to fit content - aggressive overrides */
.cell-output-display,
.cell-output,
.panel-tabset-tabby > .tab-content,
.panel-tabset > .tab-content,
.tab-pane,
.tab-pane.active,
.card-body,
.quarto-figure,
section {
  overflow: visible !important;
  height: auto !important;
  max-height: none !important;
}
/* Ensure highcharts containers respect their set height */
.highcharts-container,
.html-widget,
.htmlwidget {
  overflow: visible !important;
}
</style>
<script>
// Aggressive reflow for Highcharts - multiple attempts to catch widget initialization
(function() {
  function reflowCharts() {
    if (typeof Highcharts !== 'undefined' && Highcharts.charts) {
      Highcharts.charts.forEach(function(chart) {
        if (chart) {
          try { chart.reflow(); } catch(e) {}
        }
      });
    }
  }
  
  // Try multiple times at different intervals
  [0, 100, 250, 500, 1000, 2000].forEach(function(delay) {
    setTimeout(function() {
      window.dispatchEvent(new Event('resize'));
      requestAnimationFrame(reflowCharts);
    }, delay);
  });
  
  // Also reflow on any tab click
  document.addEventListener('click', function(e) {
    if (e.target.matches('.nav-link, [data-bs-toggle="tab"]')) {
      setTimeout(reflowCharts, 50);
    }
  });
})();
</script>
```

## Targeting Methods Analysis

This page shows how advertisers allocate their budgets across different targeting methods. Higher percentages indicate methods that receive more advertising investment.

**Key targeting categories include:**

- **Custom Audiences**: Targeting based on advertiser's own data
- **Lookalike Audiences**: Finding users similar to existing audiences
- **Detailed Targeting**: Interest and behavior-based targeting
- **Geographic**: Location-based targeting at various levels
- **Demographics**: Age, gender, and other demographic attributes


```{r setup}
#| echo: false
#| warning: false
#| message: false
#| error: false
#| results: 'hide'

# Load required libraries
library(dashboardr)
library(dplyr)
library(highcharter)

# Global chunk options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  error = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Load data
data <- readRDS('dataset_small_19obs.rds')

# Data summary
cat('Dataset loaded:', nrow(data), 'rows,', ncol(data), 'columns\n')

```


```{r}
#| echo: false
#| results: 'asis'
dashboardr::render_value_box_row(list(
  list(
    title = "Targeting Methods",
    value = "19",
    bg_color = "#2563eb",
    logo_url = "ph:target",
    logo_text = NULL
  ),
  list(
    title = "Top Method",
    value = "GEOGRAPHY: Country",
    bg_color = "#7c3aed",
    logo_url = "ph:trophy",
    logo_text = NULL
  )
))
```

## Budget Allocation by Targeting Method

```{r bar-target}
# Budget Allocation by Targeting Method
result <- create_bar(
  data = data,
  title = "Budget Allocation by Targeting Method",
  horizontal = TRUE,
  x_var = "target",
  weight_var = "perc",
  subtitle = "How advertisers allocate their budgets across different targeting strategies. Higher percentages indicate more heavily used methods.",
  y_label = "% of Total Spend",
  tooltip_prefix = "📊 Budget Share: ",
  tooltip_suffix = "% of total advertising budget",
  color_palette = "#2563eb"
)

result
```

